### 2018-03-14 paper/3-abstractions.tex
Rename section file
Work on S3

\section{Build systems, abstractly}\label{sec-compute}

@@

\definition[Correctness]{Suppose \hs{build :: Build c i k v} is a build system,
\hs{task :: Task c k v} describes an acyclic collection of build tasks, \hs{key} is an output
key, \hs{store} be a store.
Then the \hs{result}ing store \hs{result = build compute key store}
is~\emph{correct} if there exists a store \hs{ideal}, such that

\begin{itemize}
    \item The \hs{ideal} store is \emph{consistent} with \hs{task}, i.e.
    for all possible non-input keys \hs{k}, the result of executing the
    \hs{compute} matches the value in the \hs{ideal} store:
    \[
    \hs{execute}~\hs{ideal}~\hs{k}~\hs{==}~\hs{Just}~\hs{(}\hs{ideal}~\hs{k)}.
    \]
    \item The \hs{result} and \hs{ideal} agree on the output \hs{key}, i.e.
    \hs{result}~\hs{key}~\hs{==}~\hs{ideal}~\hs{key}. In other words, we require
    that the output \hs{key} has the correct value, but do not impose any
    restrictions on intermediate keys, therefore permitting shallow cloud builds.
    \item The \hs{store}, \hs{ideal} and \hs{result} all agree on the inputs
    that belong to the transitive closure of \hs{key}'s dependencies. This means
    that (i) no inputs were corrupted during the build, and (ii)~the \hs{ideal}
    store has constraints not only on the output, but also on the inputs.
\end{itemize}
}
\label{def-correct}

>>>>

\section{Build systems, abstractly}\label{sec-abstractions}

@@

\definition[Correctness]{Suppose \hs{build} is a build system, \hs{task} is a
build task description, \hs{key} is an output key, \hs{store} is an initial
store, and \hs{result} is the store produced by running the build system with
parameters \hs{task}, \hs{key} and \hs{store}. Or, using the precise language of
our abstractions:

\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
build  :: Build c i k v
task   :: Task c k v
key    :: k
store  :: Store i k v
result :: Store i k v
result = build task key store
\end{minted}
\vspace{1mm}

\noindent
Then the \hs{result} is~\emph{correct} if there exists an \hs{ideal} store, such
that:

\begin{itemize}
    \item The \hs{ideal} store is \emph{consistent} with the \hs{task}, i.e.
    for all possible non-input keys \hs{k}, the result of executing the
    \hs{task} matches the value in the \hs{ideal} store:
    \[
    \hs{execute}~\hs{task}~\hs{ideal}~\hs{k}~\hs{==}~\hs{Just}~\hs{(}\hs{ideal}~\hs{k)}.
    \]
    \item The \hs{result} and \hs{ideal} agree on the output \hs{key}, i.e.
    \hs{result}~\hs{key}~\hs{==}~\hs{ideal}~\hs{key}. In other words, we require
    that the output \hs{key} has the correct value, but do not impose any
    restrictions on intermediate keys, therefore permitting shallow cloud builds.
    \item The \hs{store}, \hs{ideal} and \hs{result} all agree on the inputs
    that belong to the transitive closure of \hs{key}'s dependencies. This means
    that (i) no inputs were corrupted during the build, and (ii)~the \hs{ideal}
    store has constraints not only on the output, but also on the inputs.
\end{itemize}
}
\label{def-correct}
